Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Adding newpage before Appendix

# Appendix: Data reading and cleaning code
```{r dashboard_file_functions, eval=FALSE}
# Data reading functions =======================================================

>>>>

\newpage
# Appendix: Data reading and cleaning code
```{r dashboard_file_functions, eval=FALSE}
# Data reading functions =======================================================
